Removing CO Interlopers from [\CII] Surveys With the Three Field Approach

### 2019-03-04 paper/ms.tex
Add intro section, separate theory section

The primary data is the observed intensity in a collection of voxels. In
practice, one will make measurements in sky coordinates and frequency space,
but to simplify the discussion we consider the observation of a finite
comoving box with volume $V$. The box is small enough that if one length is
assumed to lie along frequency space that the corresponding redshift extent of
that axis is small enough that the observed voxels can be considered
co-evolving. We are then interested in measuring $I_{l}(\bm{x})$, or the
collective emission from line $l$ from each voxel. In order to understand the
statistical properties of $I(\bm{x})$, we can compute the power spectrum which
is related to the Fourier transform of $I$,
\beq
P_{l}(k) = \avg{I(\bm{k}) I^{*}(\bm{k})}\text{.}
\eeq
Since the line intensity is a biased tracer of the underlying density field,
it is useful to parametrize the power spectrum as,
\beq
P_l(k) = b_l^2 \avg{I_l}^2 \denps{P_{\delta}}(k)\text{,}
\eeq
where $\denps{P_{\delta}}$ is the matter density power spectrum. Measuring
$b_l$ and $\avg{I_l}$ independently is a useful endeavour, but not the focus
of our study. Therefore, we will simplify and define $B_l \equiv b_l
\avg{I_l}$, such that,
\beq
P_{l}(k) = B_l^2 \denps(k)
\eeq

>>>>

\section{Introduction}\label{sec:intro}
At high redshift ($z>3$) the most promising probe of the large-scale structure
(LSS) of the universe is line intensity mapping. Rather than attempting to
resolve individual galaxies, intensity mapping aims to measure the total
emission from an atomic or molecular line of all galaxies within a rather
coarse pixel. Commonly proposed lines include H$\alpha$, H$\beta$, Ly$\alpha$,
[\CII], [\OIII], and 21~cm. During the Epoch of Reionization (EoR;
$z\gtrsim6$), the hydrogen lines also measure the bulk emission from neutral
hydrogen residing in the diffuse intergalactic medium (IGM).

\section{Theory}\label{sec:theory}
The primary data is the observed intensity in a collection of voxels. In
practice, one will make measurements in sky coordinates and frequency space,
but to simplify the discussion we consider the observation of a finite
comoving box with volume $V$. The box is small enough that if one length is
assumed to lie along frequency space that the corresponding redshift extent of
that axis is small enough that the observed voxels can be considered
co-evolving. We are then interested in measuring $I_{l}(\bm{x})$, or the
collective emission from line $l$ from each voxel. In order to understand the
statistical properties of $I(\bm{x})$, we can compute the power spectrum which
is related to the Fourier transform of $I$,
\beq
P_{l}(k) = \avg{I(\bm{k}) I^{*}(\bm{k})}\text{.}
\eeq
Since the line intensity is a biased tracer of the underlying density field,
it is useful to parametrize the power spectrum as,
\beq
P_l(k) = b_l^2 \avg{I_l}^2 \denps{P_{\delta}}(k)\text{,}
\eeq
where $\denps{P_{\delta}}$ is the matter density power spectrum. Measuring
$b_l$ and $\avg{I_l}$ independently is a useful endeavour, but not the focus
of our study. Therefore, we will simplify and define $B_l \equiv b_l
\avg{I_l}$, such that,
\beq
P_{l}(k) = B_l^2 \denps(k)
\eeq
